Classless Java

### 2015-10-19 paper/sections/Formalization.tex
Translation.

\subsection{Translation Rules}

\[ \inferrule{
  \Gamma \vdash \mixinAnn \text{ interface } C_0 \text{ extends } \overline{C} \{
  \methods \} \text{ OK }}
{ \Gamma \vdash \mixinAnn \text{ interface } C_0 \text{ extends } \overline{C} \{ \methods \} \longmapsto \\
  \mixinAnn \text{ interface } C_0 \text{ extends } \overline{C} \{ \methods; \textsf{ofMethod}(C_0); \textsf{otherMethod}(C_0) \}
} \quad \textsc{(Translation)} \]

@@

\subsubsection{Auxiliary function:???}

\begin{equation*}
\begin{array}{ll}
\textsf{ofMethod}(C_0) = ... & ... \\
\textsf{otherMethod}(C_0) = \methods_1; \methods_2 \hspace{0.1in} & \mif\ \textsf{resolve}(C_0) = \overline{field} \\
& \method_1 = \textsf{with}(field, C_0) \\
& \method_2 = \textsf{clone}(field, C_0) \\
\textsf{resolve}(C_0) = \overline{field} & \mif\ \textsf{methods}(C_0) = \mhs \\
& \forall \mh \in \mhs, \mh \textsf{ isField or isWith or isClone or isDefault} \\
& \forall field \in \overline{field},\ \mh^{field} = T\ m\oR\cR,\ \mif\ \mBody(m, C_0) = T\ m\oR\cR\QM; \\
\textsf{methods}(C_0) = \mhs\ \bigcup\ \overline{\textsf{methods}(C)} & \mif\ \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{ \methods \} \\
& \method\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@} \} \\
\textsf{with}(field, C_0) = T_0\ \QM{with}m\oR T\ x\cR\QM; & \mif\ \mh^{field} = T\ m\oR\cR,\ \mh' = T'\ \QM{with}m\oR T\ x\cR \\
& \mBody(\QM{with}m, C_0) \in \{ \mh'\QM;, \QM{default}\ \mh' \mbox{\Q@\{return \_;\}@}\} \\
& IT(T_0) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{ \methods \},\ T_0 <: T' \\
\textsf{clone}(field, C_0) = T_0\ \QM{clone}\oR\cR\QM; & \mif\ IT(T_0) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{ \methods \}
\end{array}
\end{equation*}

\haoyuan{``\textsf{isField or isWith or isClone or isDefault}''?}

>>>>

\subsection{Translation Function}

\[ [\![\mixinAnn\ \QM{interface}\ C_0\ \QM{extends}\ \Cs \oC \methods \cC ]\!] = \]
\[ \emptyset\ \QM{interface}\ C_0\ \QM{extends}\ \Cs \oC \methods;\ \ofMethod(C_0);\ \otherMethod(C_0) \cC \]

@@

\subsubsection{Auxiliary function: $\ofMethod(C_0)$, $\otherMethod(C_0)$}

\begin{equation*}
\begin{array}{ll}
\ofMethod(C_0) = \QM{static}\ C_0\ \QM{of} \oR T_1\ m_1\QM,\ldots T_k\ m_k\cR\ \QM{\{} &  \\
\ \ \ \ \QM{return new}\ C_0 \oR\cR\ \QM{\{}  & \mif\ \resolve(C_0) = \methods \\
\ \ \ \ \ \ \ \ T_1\ \_m_1 = m_1\QM;\ldots T_k\ \_m_k = m_k\QM; & \forall \method_i \in \methods, \method_i = T_i\ m_i\oR\cR\QM; \\
\ \ \ \ \ \ \ \ T_i\ m_i\oR\cR\ \QM{\{return}\ \_m_i\QM{;\}}\ \ldots & T_i\ m_i\oR\cR \text{ included for all } i \\
\ \ \ \ \ \ \ \ C_0\ \QM{with}m_i\oR T_i\ x_i\cR\ \QM{\{} & C_0\ \QM{with}m_i\oR T_i\ x_i\cR \text{ included if }\with(\method_i, C_0) \text{ defined} \\
\ \ \ \ \ \ \ \ \ \ \ \ \QM{return this.of}\oR m_1\oR\cR\QM,\ldots x_i\QM,\ldots m_k\oR\cR\cR\QM{;} & \\
\ \ \ \ \ \ \ \ \QM{\}}\ \ldots & \\
\ \ \ \ \ \ \ \ C_0\ \QM{clone}\oR\cR\ \QM{\{} & C_0\ \QM{clone}\oR\cR \text{ included if }\clone(C_0) \text{ defined} \\
\ \ \ \ \ \ \ \ \ \ \ \ \QM{return this.of}\oR m_1\oR\cR\QM,\ldots m_k\oR\cR \cR\QM; & \\
\ \ \ \ \ \ \ \ \QM{\}} & \\
\ \ \ \ \QM{\};} & \\
\QM{\}} & \\
\otherMethod(C_0) = \overline{\with(\method, C_0)}; \clone(C_0) \hspace{0.1in} & \mif\ \textsf{resolve}(C_0) = \methods \\
\resolve(C_0) = \{\mBody(m, C_0)\ |\ \mBody(m, C_0)\ \isField\} & \forall m\in\dom(C_0), \text{one case is satisfied:} \\
& (1)\ \mBody(m, C_0)\ \isField \\
& (2)\ \mBody(m, C_0)\ \isWith \\
& (3)\ \mBody(m, C_0)\ \isClone \\
& (4)\ \mBody(m, C_0)\ \isDefault \\
\mBody(m, C_0)\ \isField & \mif\ \mBody(m, C_0) = T\ m\oR\cR\QM;\ m\ne\QM{clone} \\
\mBody(m, C_0)\ \isWith & \mif\ \mh^{\mBody(m, C_0)} = T'\ \QM{with}m' \oR T\ x\cR, C_0 <: T' \\
& \mand\ \mBody(m', C_0) = T\ m'\oR\cR\QM;\ m'\ne\QM{clone} \\
\mBody(m, C_0)\ \isClone & \mif\ \mh^{\mBody(m, C_0)} = T\ \QM{clone}\oR\cR, C_0 <: T \\
\mBody(m, C_0)\ \isDefault & \mif\ \mBody(m, C_0) = \QM{default}\ \mh\mbox{\Q@\{return \_;\}@} \\
\with(\method, C_0) = C_0\ \QM{with}m\oR T\ x\cR\QM; & \mif\ \method = T\ m\oR\cR\QM;\ \mBody(\QM{with}m, C_0)\ \isWith \\
\clone(C_0) = C_0\ \QM{clone}\oR\cR\QM; & \mif\ \mBody(\clone, C_0)\ \isClone \\
\end{array}
\end{equation*}
